Viscous Transport in Eroding Porous Media

### 2019-09-30 docs/transport/erosion_transport.tex
fixed merge conflicts

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Boundary Integral Equation Formulation}
\label{sec:DLP}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\nick{To solve} the incompressible Stokes
equations in complex two-dimensional porous media, we \nick{reformulate\st{d}} the incompressible Stokes equations as a BIE.  This has the advantage that
only the one-dimensional boundary of the domain must be discretized, and,
\nick{with an appropriate quadrature formula and fast summation methods,
the result is a high-fidelity numerical simulation of near-optimal computational complexity.}

\subsection{Double-Layer Potential Formulation in $\RR^2$}
Applying the same approach as our previous work~\cite{qua-moo2018}, we
write the velocity $\uu$ as a double-layer potential 
\begin{align}
  \DDD[\eeta](\xx) = \int_{\bd\Omega} D(\xx,\yy) \eeta(\yy)\, ds_\yy = 
  \frac{1}{\pi}\int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
  \label{eqn:velocityDLP}
\end{align}
where $D$ is \nick{\st{an} a} kernel of the integral operator, $\rr = \xx - \yy$,
$\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
is an unknown density function.  The double-layer potential can not
represent all solutions of the incompressible Stokes equations, so we
complete the integral equation formulation by adding the Stokeslets and
rotlets~\cite{pow-mir1987}
\begin{align}
  S[\llambda_\ell,\cc_\ell](\xx) = \frac{1}{4\pi} \left( 
    -\log \rho \II + \frac{\rr \otimes \rr}{\rho^2}
    \right)\llambda_\ell, \quad
  R[\xi_\ell,\cc_\ell](\xx) = \frac{\rr^\perp}{\rho^2} \xi_\ell,
\end{align}
where $\rr = \xx - \cc_\ell$, $\cc_\ell$ is a point inside the
$\ell^{th}$ eroding body, $\rr^\perp = (r_2,-r_1)$, and $\rho =
\|\rr\|$.  Then, for any sufficiently smooth geometry $\Omega$, the
solution of the incompressible Stokes equation with a Dirichlet boundary
condition $\ff$ is
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) + 
    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx), \quad \xx \in \Omega,
\end{align}
where the density function, Stokeslets, and rotlets satisfy
\begin{subequations}
\label{eqn:BIE}
\begin{alignat}{3}
  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx) +
    \NN_0[\eeta](\xx), \quad &&\xx \in \bd\Omega, \\
  \llambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
    \eeta(\yy)\, ds_\yy &&\ell = 1,\ldots,M, \\
  \xi_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell}
    (\yy - \cc_\ell)^\perp \cdot \eeta(\yy)\, ds_\yy 
    &&\ell = 1,\ldots,M.
\end{alignat}
\end{subequations}
The operator $\NN_0$ is the integral operator with kernel
$N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in \Gamma$,
which removes the rank one null space \nick{\st{resulting} that results} from the flux-free
requirement of $\ff$.  In this work, $\ff$ is the prescribed velocity,
$\UU$, on the outer wall, $\Gamma$, and is zero on the eroding bodies,
$\gamma_\ell$, $\ell=1,\ldots,M$.

Once~\eqref{eqn:BIE} is solved for the density function $\eeta$, the
Stokeslets $\llambda_\ell$, and the rotlets $\xi_\ell$, \nick{we are able to compute the deformation tensor, pressure, and vorticity, defined respectively as}
\begin{align}
  \label{eqn:deformationDLP} 
  \ssigma(\xx) &= \int_{\bd\Omega} \mathbf{D}_{\ssigma}(\xx,\yy) 
      \eeta(\yy) ds_{\yy} 
  = \frac{1}{2\pi}\int_{\bd\Omega} \left(
    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn) 
    \right. \nonumber \\
    & \qquad\qquad\qquad\qquad\qquad\qquad \left.
    +\frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
    \right) \, ds_\yy, \\
%
  p(\xx) &= \int_{\bd\Omega} D_{p}(\xx,\yy) 
      \eeta(\yy) ds_{\yy} 
  = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) \nn \cdot
      \eeta(\yy)\,ds_\yy, \\
%
  \label{eqn:vorticityDLP} 
  \omega(\xx) &= \int_{\bd\Omega} D_{\omega}(\xx,\yy) 
      \eeta(\yy) ds_{\yy} 
  = -\frac{1}{\pi} \int_{\bd\Omega}
    \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4} 
      (\rr \cdot \eeta) \, ds_\yy,
\end{align}
\nick{\st{We require the deformation tensor of the double-layer potential at
$\xx \in \bd \Omega$.}}
Since the deformation tensor of the double-layer potential is discontinuous across the boundary $\bd\Omega$, the jump term 
\begin{align}
  \frac{1}{2} \left(\pderiv{\eeta}{\ss} \cdot \ss \right) \left[
    \begin{array}{cc}
      s_x^2 - s_y^2 & 2s_x s_y \\ 2s_x s_y & s_y^2 - s_x^2
    \end{array}
  \right],
  \label{eqn:deformationJump}
\end{align}
must be added to $\ssigma(\xx)$ for $\xx \in \bd\Omega$.  Finally, the
Stokeslets and rotlets \nick{do not exhibit such jumps, and so the associated components of the deformation tensor, pressure, and vorticity} are straightforward to compute~\cite{poz1992}.  Having computed
the deformation tensor on $\gamma$, the shear stress is computed as
defined in equation~\eqref{eqn:shearStress}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Double-Layer
Potential}
\label{sec:DLPcomplex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In equations~\eqref{eqn:velocityDLP} and~\eqref{eqn:deformationDLP},
$\uu$ and its deformation tensor are written as layer potentials in
$\RR^2$.  However, the quadrature method we introduce in
Section~\ref{sec:method} requires a complex-valued representation of the
layer potentials. The first step is to write the Laplace double-layer
potential as the complex integral
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2}\eeta(\yy)\, ds_\yy = \Re (v(x)) \quad 
    \text{where} \quad v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x - y} \, dy,
  \label{eqn:laplaceComplex}
\end{align}
where $\xx,\yy \in \RR^2$ are identified with the points $x,y \in \CC$.
Equation~\eqref{eqn:laplaceComplex} is converted to a Cauchy
integral by first finding the boundary data of $v$.  Assuming that
$\Omega$ is a simply-connected interior domain, the boundary data
of $v$ satisfies the Sokhotski-Plemelj jump relation
\begin{align}
  \label{eqn:SPrelation}
  v(x) = - \frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
\end{align}
For exterior domains, the jump term changes from $-1/2$ to $1/2$, and
for multiply-connected domains, such as a porous media, $\bd\Omega$ is
decomposed into its different connected components and the appropriate
Cauchy integral is evaluated.  Since $v$ is a holomorphic function and
we have its boundary data, by the Cauchy integral theorem we have
\begin{align}
  \label{eqn:cauchy}
  v(x) = \frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{v(y)}{y-x} \,dy, \quad
  v'(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^2} \, dy, \quad
  v''(x) = \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^3} \, dy,
\end{align}
for $x \in \Omega$.  Since $v(x)$ depends on the complex-valued density
function $\eta$, we use the notation $v[\eta](x)$ to denote the
holomorphic function defined in equation~\eqref{eqn:laplaceComplex}, and
its first two derivatives are written as $v'[\eta](x)$ and
$v''[\eta](x)$.

To rewrite the Stokes double-layer potential~\eqref{eqn:velocityDLP} in
terms of Cauchy integrals and their derivatives, we start by converting
it into a sequence of Laplace layer potentials~\cite{bar-wu-vee2015}
\begin{equation}
  \label{eqn:Stokes2Laplace}
  \begin{aligned}
    \DDD[\eeta](\xx) &= 
      \frac{1}{2\pi} \int_{\bd\Omega} 
        \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
      \frac{1}{2\pi} \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
      &- \frac{1}{2\pi} x_1 \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
      \frac{1}{2\pi} x_2 \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
  \end{aligned}
\end{equation}
Therefore, the Stokes double-layer potential can be written in terms of
Cauchy integrals and their first derivative as
\begin{equation}
  \begin{aligned}
    u_1(x) &= \Re (v[\psi_1](x)) + \Re (v'[y\cdot\eta](x)) 
             -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)), \\
    u_2(x) &= \Re (v[\psi_2](x)) - \Im (v'[y\cdot\eta](x)) 
         +x_1\Im (v'[\eta_1](x)) + x_2\Im (v'[\eta_2](x)),
  \end{aligned}
  \label{eqn:cauchyVelocity}
\end{equation}
where $y \cdot \eta = y_1 \eta_1 + i y_2 \eta_2 \in \CC$, 
\begin{align} 
  \psi_1=(\eta_1+i\eta_2)\frac{\Re(n)}{n}, \quad
  \psi_2=(\eta_1+i\eta_2)\frac{\Im(n)}{n},
\end{align}
and $n \in \CC$ is the complex representation of the outward unit normal
$\nn \in \RR^2$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Boundary Integral Equation Formulation}
\label{sec:DLP}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Since we require an accurate solution of the incompressible Stokes
equations in complex two-dimensional geometries, we reformulate the
incompressible Stokes equations as a BIE.  This has the advantage that
only the one-dimensional boundary of the domain must be discretized,
and, with an appropriate quadrature formula and fast summation methods,
the result is a high-fidelity numerical simulation of near-optimal
computational complexity.

\subsection{Double-Layer Potential Formulation in $\RR^2$}
Applying the same approach as our previous work~\cite{qua-moo2018}, we
write the velocity $\uu$ as a double-layer potential 
\begin{align}
  \DDD[\eeta](\xx) = \int_{\bd\Omega} D(\xx,\yy) \eeta(\yy)\, ds_\yy = 
  \frac{1}{\pi}\int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
  \label{eqn:velocityDLP}
\end{align}
where $D$ is \nick{\st{an} a} kernel of the integral operator, $\rr =
\xx - \yy$, $\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$,
and $\eeta$ is an unknown density function.  The double-layer potential
can not represent all solutions of the incompressible Stokes equations,
so we complete the integral equation formulation by adding the $M$
Stokeslets and rotlets~\cite{pow-mir1987}
\begin{align}
  S[\llambda_\ell,\cc_\ell](\xx) = \frac{1}{4\pi} \left( 
    -\log \rho \II + \frac{\rr \otimes \rr}{\rho^2}
    \right)\llambda_\ell, \quad
  R[\xi_\ell,\cc_\ell](\xx) = \frac{\rr^\perp}{\rho^2} \xi_\ell,
\end{align}
where $\rr = \xx - \cc_\ell$, $\cc_\ell$ is a point inside the
$\ell^{th}$ eroding body, $\rr^\perp = (r_2,-r_1)$, and $\rho =
\|\rr\|$.  Then, for any sufficiently smooth geometry $\Omega$, the
solution of the incompressible Stokes equation with a Dirichlet boundary
condition $\ff$ is
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) + 
    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx), \quad \xx \in \Omega,
\end{align}
where the density function, Stokeslets, and rotlets satisfy
\begin{subequations}
\label{eqn:BIE}
\begin{alignat}{3}
  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
    \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx) + 
    \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx) +
    \NN_0[\eeta](\xx), \quad &&\xx \in \bd\Omega, \\
  \llambda_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell} 
    \eeta(\yy)\, ds_\yy &&\ell = 1,\ldots,M, \\
  \xi_\ell &= \frac{1}{2\pi} \int_{\gamma_\ell}
    (\yy - \cc_\ell)^\perp \cdot \eeta(\yy)\, ds_\yy 
    &&\ell = 1,\ldots,M.
\end{alignat}
\end{subequations}
Here, the null space associated with the flux-free condition of $\ff$ is
addressed with the integral operator $\NN_0$ which has the integral
kernel $N_0(\xx,\yy) = \nn(\xx) \otimes \nn(\yy)$, $\xx,\yy \in \Gamma$.
In this work, $\ff$ is the prescribed velocity, $\UU$, on the outer
wall, $\Gamma$, and is zero on the eroding bodies, $\gamma_\ell$,
$\ell=1,\ldots,M$.

Once~\eqref{eqn:BIE} is solved for the density function $\eeta$, the
Stokeslets $\llambda_\ell$, and the rotlets $\xi_\ell$, \nick{we are able to compute the deformation tensor, pressure, and vorticity, defined respectively as}
\begin{align}
  \label{eqn:deformationDLP} 
  \ssigma(\xx) &= \int_{\bd\Omega} \mathbf{D}_{\ssigma}(\xx,\yy) 
      \eeta(\yy) ds_{\yy} 
  = \frac{1}{2\pi}\int_{\bd\Omega} \left(
    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn) 
    \right. \nonumber \\
    & \qquad\qquad\qquad\qquad\qquad\qquad \left.
    +\frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
    \right) \, ds_\yy, \\
%
  p(\xx) &= \int_{\bd\Omega} D_{p}(\xx,\yy) 
      \eeta(\yy) ds_{\yy} 
  = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) \nn \cdot
      \eeta(\yy)\,ds_\yy, \\
%
  \label{eqn:vorticityDLP} 
  \omega(\xx) &= \int_{\bd\Omega} D_{\omega}(\xx,\yy) 
      \eeta(\yy) ds_{\yy} 
  = -\frac{1}{\pi} \int_{\bd\Omega}
    \frac{(\rr \cdot \nn^\perp) + (\rr \cdot \nn)}{\rho^4} 
      (\rr \cdot \eeta) \, ds_\yy,
\end{align}
respectively.  Since the deformation tensor of the double-layer
potential is discontinuous across $\bd\Omega$, the jump term 
\begin{align}
  \frac{1}{2} \left(\pderiv{\eeta}{\ss} \cdot \ss \right) \left[
    \begin{array}{cc}
      s_x^2 - s_y^2 & 2s_x s_y \\ 2s_x s_y & s_y^2 - s_x^2
    \end{array}
  \right],
  \label{eqn:deformationJump}
\end{align}
must be added to $\ssigma(\xx)$ for $\xx \in \bd\Omega$.
Finally, the Stokeslets and rotlets do not exhibit any jumps
across $\gamma$, and so the associated components of the deformation tensor, pressure, and vorticity due to the Stokeslets
and rotlets are straightforward to compute~\cite{poz1992}.  Having
computed the deformation tensor on $\gamma$, the shear stress is
computed as defined in equation~\eqref{eqn:shearStress}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Double-Layer
Potential}
\label{sec:DLPcomplex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In equations~\eqref{eqn:velocityDLP} and~\eqref{eqn:deformationDLP},
$\uu$ and its deformation tensor are written as layer potentials in
$\RR^2$, but the quadrature method we introduce in
Section~\ref{sec:method} requires a complex-valued representation of the
layer potentials. The first step is to write the Laplace double-layer
potential as the complex integral
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2}\eeta(\yy)\, ds_\yy = \Re (v(x)) \quad 
    \text{where} \quad v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x - y} \, dy,
  \label{eqn:laplaceComplex}
\end{align}
where $\xx,\yy \in \RR^2$ are identified with the points $x,y \in \CC$,
and $\eta$ is the complex-valued counterpart of $\eeta$.
Equation~\eqref{eqn:laplaceComplex} is converted to a Cauchy integral by
first finding the boundary data of $v$.  Assuming that $\Omega$ is a
simply-connected interior domain, the boundary data of $v$ satisfies the
Sokhotski-Plemelj jump relation
\begin{align}
  \label{eqn:SPrelation}
  v(x) = - \frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
\end{align}
For exterior domains, the jump term changes from $-1/2$ to $1/2$, and
for multiply-connected domains, such as a porous media, $\bd\Omega$ is
decomposed into its different connected components and the appropriate
jump relation is applied.  Since $v$ is a holomorphic function and we
have its boundary data, by the Cauchy integral theorem we have
\begin{align}
  \label{eqn:cauchy}
  v(x) = \frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{v(y)}{y-x} \,dy, \quad
  v'(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^2} \, dy, \quad
  v''(x) = \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^3} \, dy,
\end{align}
for $x \in \Omega$.  Since $v(x)$ depends on the complex-valued density
function $\eta$, we use the notation $v[\eta](x)$ to denote the
holomorphic function defined in equation~\eqref{eqn:laplaceComplex}, and
its first two derivatives are written as $v'[\eta](x)$ and
$v''[\eta](x)$.

To rewrite the Stokes double-layer potential~\eqref{eqn:velocityDLP} in
terms of Cauchy integrals and their derivatives, we start by converting
it into a sequence of Laplace layer potentials~\cite{bar-wu-vee2015}
\begin{equation}
  \label{eqn:Stokes2Laplace}
  \begin{aligned}
    \DDD[\eeta](\xx) &= 
      \frac{1}{2\pi} \int_{\bd\Omega} 
        \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
      \frac{1}{2\pi} \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
      &- \frac{1}{2\pi} x_1 \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
      \frac{1}{2\pi} x_2 \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy,
  \end{aligned}
\end{equation}
where $\xx = (x_1,x_2)$. Therefore, the Stokes double-layer potential
can be written as a sum of Cauchy integrals and its first derivative 
\begin{equation}
  \begin{aligned}
    u_1(x) &= \Re (v[\psi_1](x)) + \Re (v'[y\cdot\eta](x)) 
             -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)), \\
    u_2(x) &= \Re (v[\psi_2](x)) - \Im (v'[y\cdot\eta](x)) 
         +x_1\Im (v'[\eta_1](x)) + x_2\Im (v'[\eta_2](x)),
  \end{aligned}
  \label{eqn:cauchyVelocity}
\end{equation}
where $y \cdot \eta = y_1 \eta_1 + i y_2 \eta_2 \in \CC$, 
\begin{align} 
  \psi_1=(\eta_1+i\eta_2)\frac{\Re(n)}{n}, \quad
  \psi_2=(\eta_1+i\eta_2)\frac{\Im(n)}{n},
\end{align}
and $n \in \CC$ is the complex representation of the outward unit normal
$\nn \in \RR^2$.
